Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-04-25 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
VSTTE 2020 paper update

In order to evaluate a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose tools, e.g., MATLAB/Simulink~\cite{Gow1999}. However, these tools are based on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations, and potential failures of a system are infeasible~\cite{ClarkeHV18}. Non-linear optimization tools could be employed since a PV system is typically modeled as a non-linear set of equations. However, the industry demands the final solution to be the optimum, considering manufacturers, models, and brands available on the market and not just minimum or maximum powers and values for the optimized items, which can only be achieved with specialist PV optimization software.

Optimization of PV systems is not a recent topic; since the 1990s, different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods, were proposed and developed~\cite{Alsadi2018}. In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}. In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}. In $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}. In $2019$, an automated verification methodology was proposed to validate stand-alone solar PV systems~\cite{TrindadeCordeiro19}. However, \textit{formal methods and its application to synthesize PV systems are still unexplored in literature}.

@@

A PV system is illustrated in Fig.\ref{fig:blockdiagram}. It employs the PV generator (\textit{panel or an array}), which is a semiconductor device that can convert solar energy into DC electricity. For night hours or rainy days, we hold \textit{batteries}, where power can be stored and used. The use of batteries as a storage form implies the presence of a \textit{charge controller}~\cite{Hansen}. The PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion is required (\textit{inverter}). The \textit{AC load} dictates the behavior of the AC electrical load from the house that will be fed by the system.

@@

All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB RAM, running Ubuntu $16.04$ LTS $64$-bits. For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB RAM running Windows 10. The hardware platform was not the same because of the availability of the machines; this has an impact on performance, which is less favourable to HOMER Pro. PVsyst used the same configuration as HOMER Pro. We perform the experiments with a predefined time out of $660$ minutes.

@@

Each simulation with PVsyst took $4$ seconds. We were unable to validate case study $3$ using PVsyst since the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a 24 h minimum autonomy). Case studies $2$ and $7$ had only HOMER Pro sizing validation, because there exists no deployed equivalent system in the field, and the synthesis technique did not present a solution due to time-out and internal failures in the underlying verification engine. %(our technique presented a \textit{time out} in case study $2$ and an \textit{UNSAT} in the case study $7$).

>>>>

In order to evaluate a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose tools, e.g., MATLAB/Simulink~\cite{Gow1999}. However, these tools are based on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations, and potential failures of a system are infeasible~\cite{ClarkeHV18}. Non-linear optimization tools could be employed since a PV system is typically modelled as a non-linear set of equations. However, the industry demands the final solution to be the optimum, considering manufacturers, models, and brands available on the market and not just minimum or maximum powers and values for the optimized items, which can only be achieved with specialist PV optimization software.

Optimization of PV systems is not a recent topic; since the 1990s, different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods, were proposed and developed~\cite{Alsadi2018}. In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}. In $2017$, a researcher suggested the application of formal methods to verify and control the behaviour of computational devices in a smart grid ~\cite{Abate2017}. In $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}. In $2019$, an automated verification methodology was proposed to validate stand-alone solar PV systems~\cite{TrindadeCordeiro19}. However, \textit{formal methods and its application to synthesize PV systems are still unexplored in literature}.

@@

A PV system is illustrated in Fig.\ref{fig:blockdiagram}. It employs the PV generator (\textit{panel or an array}), which is a semiconductor device that can convert solar energy into DC electricity. For night hours or rainy days, we hold \textit{batteries}, where power can be stored and used. The use of batteries as a storage form implies the presence of a \textit{charge controller}~\cite{Hansen}. The PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion is required (\textit{inverter}). The \textit{AC load} dictates the behaviour of the AC electrical load from the house that will be fed by the system.

@@

All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB RAM, running Ubuntu $16.04$ LTS $64$-bits. For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB RAM running Windows 10. The hardware platform was not the same because of the availability of the machines; this has an impact on performance, which is less favourable to HOMER Pro. PVsyst used the same configuration as HOMER Pro. We perform the experiments with a predefined \textit{time out} of $660$ minutes.

@@

Each simulation with PVsyst took $4$ seconds. We were unable to validate case study $3$ using PVsyst since the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a 24 h minimum autonomy). Case studies $2$ and $7$ had only HOMER Pro sizing validation, because there exists no deployed equivalent system in the field, and the synthesis technique did not present a solution due to \textit{time out} and internal failures in the underlying verification engine. %(our technique presented a \textit{time out} in case study $2$ and an \textit{UNSAT} in the case study $7$).
